---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)

library(tidyverse)
```

# wtmapi

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
<!-- badges: end -->


The goal of `wtmapi` is to provide access to the [public data API](https://data-api.whotargets.me/docs/) of [Who Targets Me](https://whotargets.me/en/).     

## Installation

You can install the released version of wtmapi from [GitHub](https://github.com/favstats/wtmapi) with:

``` r
# install.packages("remotes")
remotes::install_github("favstats/wtmapi")
```

## Examples


```{r example}
library(wtmapi)
```

The main function in `wtmapi` to use is **`wtm_get`**. With it you can access the API endpoints:

+ `candidates-impressions`
+ `candidates-targeting-methods`
+ `impressions-daily-totals`


Here are some basic examples which show you how to solve a common problems. If you have questions, refer to the [docs](https://data-api.whotargets.me/docs/) which will help you with the query parameter.

### Retrieve impressions

Let's say we want to retrieve all ads with *l*ess *t*han (**lt**) 20 impressions from the party "CDU" in Germany:

```{r}
impressions_dat <- wtm_get(endpoint = "candidates-impressions", 
               country = "DE", 
               party = "CDU",
               lt = list(impressions = 20))

impressions_dat


```



### Retrieve targeting methods

Let's say we want to retrieve all ads which have *g*reater *t*han or *e*qual (**gte**) to 1 `bct` (which is the behavioral targeting method) in the US:

```{r}
targeting_dat <- wtm_get(endpoint = "candidates-targeting-methods", 
                         country = "US",
                         gte = list(bct = 1))

targeting_dat

```

### Retrieve daily totals

Retrieve the daily total impressions for a country (in this case germany):


```{r}
daily_totals <- wtm_get(endpoint = "impressions-daily-totals", 
                        country = "DE")

daily_totals


```

## TODO

+ Include pagination
+ Improve documentation
